---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nicheDE)
```


# Niche-DE-Tutorial
This repository contains a tutorial for using the nicheDE package in R. Each step in the nicheDE process is described in detail; from the initial deconvolution step to downstream processes such as niche ligand-receptor analysis. Click the links below to visit a specific step in the pipeline.

+ [Installation](articles/Installation): How to download Niche-DE  using devtools.
+ [Deconvolution](articles/Deconvolution): A step by step guide for performing cell type deconvolution of your spatial transcriptomic data using RCTD.
+ [Average Expression Profile Calculation](articles/AverageExpressionProfile): A guide on how to calculate the average expression profile matrix from your reference dataset.
+ [Object Creation](articles/ObjectCreation): A guide on how to create your own niche-DE object starting from a [spatial seurat object](https://github.com/Kmason23/Niche-DE-Tutorial/tree/main/ObjectCreation/FromSeurat) or [raw data matrices](https://github.com/Kmason23/Niche-DE-Tutorial/tree/main/ObjectCreation/FromRaw).
+ [Effective Niche Calculation](https://github.com/Kmason23/Niche-DE-Tutorial/tree/main/EffectiveNicheCalculation): A guide on how to calculate the effective niche as well as suggested guidelines on how to choose the kernel bandwidth.
+ [Performing Niche-DE](https://github.com/Kmason23/Niche-DE-Tutorial/tree/main/PerformingNicheDE): A guide on how to run niche-DE once you have your niche-DE object.
+ [Getting Niche-DE Genes](https://github.com/Kmason23/Niche-DE-Tutorial/tree/main/GettingNicheDEGenes): A guide on how to get niche-DE genes between a given index and niche cell type as well as how to perform pathway enrichment analysis given these niche-DE genes.
+ [Marker Genes](https://github.com/Kmason23/Niche-DE-Tutorial/tree/main/MarkerGenes): A guide on performing marker gene analysis using niche-DE
+ [Ligand Receptor Analysis](https://github.com/Kmason23/Niche-DE-Tutorial/tree/main/LigandReceptorAnalysis): A guide on performing ligand-receptor analysis using niche-DE.
